Software Ticket Quality

### 2017-11-20 proposal/mprop.tex
Add paper on bug report severity analysis

>>>>

\textbf{Predicting the severity of a reported bug}\cite{lamkanfi2010predicting}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The main goal of the research was to determine if, using textual analysis, one can
    predict the severity of a bug. This main research question was further divided into
    4 RQs:
      \begin{itemize}
        \item which terms in the textual description could serve as good indicators for
        the bug severity;
        \item what types of textual fields (e.g. summary, description) serve indicate the
        bug severity best;
        \item how many sample does one need to train an accurate predictor;
        \item is it better to have a specialized predictor for each component or combine
        bug reports over multiple components.
      \end{itemize}
  \item \textbf{What was the method?}
    The authors conducted their research on the Mozilla, Eclipse and GNOME project. The 
    approach can be divided into 5 steps:
      \begin{itemize}
        \item extract and organize bug reports;
        \item preprocess bug reports (i.e. tokenization, stop word removal and stemming);
        \item train the classifier on multiple datasets of bug reports (they used a ratio of
        70\% - training, 30\% - evaluation);
        \item apply the trained classifier on the evaluation set.
      \end{itemize}
        Then, they used precision and recall to evaluate their results.
  \item \textbf{What did they learn?}
    The authors managed to answer all their 4 research questions:
      \begin{itemize}
        \item terms such as deadlock, hand, crash, memory or segfault usually indicate a severe bug;
        however, there are other terms that can indicate the opposite (i.e. non-severe bugs),
        such as typo;
        \item they switched from analysing only the one-line summary to analysing the whole
        textual description as it contains more detailed information, thus the model can be
        trained better; however, when they analysed the results and noticed that they had a large
        number of false positives, which made them switch back to one-line summaries;
        \item the classifier needs a large number of datasets in order to predict better on the
        evaluation set;
        \item it mainly depends on the type of project and how it is structured; thus, in Mozilla
        and GNOME, which share problem-specific characteristics over different components, using a 
        predictor across components sees improvements; however, the dataset needs to be even larger,
        otherwise the performance starts to decrease.
      \end{itemize}
  \item \textbf{Relevance to our work}:
    The authors' findings could help us in better understanding textual description analysis and how
    it can indicate various aspects about a ticket, such as severity. Thus, we can apply the technique
    described in order to differentiate between severe and non-severe bug reports so that we can 
    focus on a specific category in our own research, if we want that.
\end{itemize}
